Reproduction frequency and offspring survival decline in elephant seals past prime age

### 2024-07-11 paper/paperv3.qmd
Updating plots with sample sizes and making other edits

---
title: "Reproduction frequency and offspring survival decline in elephant seals past prime age"
format: 
  html: 
    echo: false
    fig-width: 5
    fig-height: 5
    code-fold: true
    code-tools: true
    warning: false
    toc: true
editor: visual
bibliography: references.bib
---

@@

# Create POPULATION-LEVEL (i.e. without rand effects) predictions
breed_pred_pop <- ggpredict(breed_age_mod, 
                            terms = c("age10 [all]", "age_cat")) %>% 
  as_tibble() %>% 
  mutate(age = x * 10 + age_senesce,
         age_cat = factor(group, levels = c("Young", "Old"))) %>% 
  filter((age_cat == "Young" & age < age_senesce) |
           (age_cat == "Old" & age >= age_senesce),
         age <= 20)

@@

ggplot(breed_pred_pop, aes(age, predicted)) +
  geom_line(aes(group = interaction(age_cat, year_fct)),
            breed_pred_years,
            alpha = 0.1) +
  geom_ribbon(aes(fill = age_cat, ymin = conf.low, ymax = conf.high), 
              alpha = 0.5) +
  geom_line(aes(color = age_cat), linewidth = 1.2) +
  geom_line(aes(color = age_cat),
            breed_pred_wgt, 
            linewidth = 1.2,
            linetype = "dashed") +
  geom_pointrange(aes(y = perc_breed,
                      ymin = perc_breed - se,
                      ymax = perc_breed + se),
                  breed_nonbreed) +
  geom_vline(xintercept = age_senesce - 0.5, linetype = "dashed") +
  scale_y_continuous("Breeding", labels = scales::percent) +
  scale_color_manual(values = c("#7fbc41", "#de77ae")) +
  scale_fill_manual(values = c("#7fbc41", "#de77ae")) +
  labs(x = "Age (years)") +
  theme(legend.position = "none")
```

@@

```{r}
#| label: fig-repro-age
#| fig-width: 9

n_recruit <- surv_recr_data %>% 
  filter(pupsex == "F")

@@

# Create pup survival POPULATION-LEVEL (i.e. without rand effects) predictions
surv_pred_pop <- ggpredict(
  pup_surv_mod, 
  terms = c("age10 [all]", "age_cat"),
  type = "fixed",
  interval = "confidence"
) %>% 
  as_tibble() %>% 
  mutate(age = x * 10 + age_senesce,
         age_cat = group) %>% 
  filter((age_cat == "Young" & age < age_senesce) |
           (age_cat == "Old" & age >= age_senesce),
         age <= 20)

@@

fig_surv <- ggplot(surv_pred_pop, aes(age, predicted)) +
  geom_line(aes(group = interaction(age_cat, year_fct)),
            surv_pred_years,
            alpha = 0.1) +
  geom_ribbon(aes(fill = age_cat, ymin = conf.low, ymax = conf.high), 
              alpha = 0.2) +
  geom_line(aes(color = age_cat, linetype = age_cat), linewidth = 1.2) +
  geom_pointrange(aes(y = perc_surv, 
                      ymin = perc_surv - se_surv, 
                      ymax = perc_surv + se_surv),
                  surv_recr_summ) +
  geom_vline(xintercept = age_senesce - 0.5, linetype = "dashed") +
  scale_y_continuous("Offspring survival", 
                     labels = scales::percent,
                     limits = c(0, 0.62)) +
  scale_color_manual(values = c("#7fbc41", "#de77ae")) +
  scale_fill_manual(values = c("#7fbc41", "#de77ae")) +
  scale_linetype_manual(values = c("dashed", "solid")) +
  labs(x = "Age (years)") +
  theme(legend.position = "none")

# Create pup recruit POPULATION-LEVEL (i.e. without rand effects) predictions
recr_pred_pop <- ggpredict(
  pup_recr_mod, 
  terms = c("age10 [all]", "age_cat"),
  type = "fixed",
  interval = "confidence"
) %>% 
  as_tibble() %>% 
  mutate(age = x * 10 + age_senesce,
         age_cat = group) %>% 
  filter((age_cat == "Young" & age < age_senesce) |
           (age_cat == "Old" & age >= age_senesce),
         age <= 20)

@@

fig_recr <- ggplot(recr_pred_pop, aes(age, predicted)) +
  geom_line(aes(group = interaction(age_cat, year_fct)),
            recr_pred_years,
            alpha = 0.1) +
  geom_ribbon(aes(fill = age_cat, ymin = conf.low, ymax = conf.high), 
              alpha = 0.2) +
  geom_line(aes(color = age_cat), linewidth = 1.2, linetype = "dashed") +
  geom_pointrange(aes(y = perc_recr, 
                      ymin = perc_recr - se_recr, 
                      ymax = perc_recr + se_recr),
                  surv_recr_summ) +
  geom_vline(xintercept = age_senesce - 0.5, linetype = "dashed") +
  scale_y_continuous("Offspring recruitment", 
                     labels = scales::percent,
                     limits = c(0, 0.62)) +
  scale_color_manual(values = c("#7fbc41", "#de77ae")) +
  scale_fill_manual(values = c("#7fbc41", "#de77ae")) +
  labs(x = "Age (years)") +
  theme(legend.position = "none")

(fig_surv | fig_recr) + plot_annotation(tag_levels = "A")

@@

# Create POPULATION-LEVEL (i.e. without rand effects) predictions
sexrat_pred <- ggpredict(sexrat_age_mod, 
                         terms = c("age10 [all]", "age_cat")) %>% 
  as_tibble() %>% 
  mutate(age = x * 10 + age_senesce,
         age_cat = factor(group, levels = c("Young", "Old"))) %>% 
  filter((age_cat == "Young" & age < age_senesce) |
           (age_cat == "Old" & age >= age_senesce))

@@

ggplot(sexrat_pred, aes(age, predicted)) +
  geom_line(aes(group = interaction(age_cat, year_fct)),
            sexrat_pred_years,
            alpha = 0.1) +
  geom_ribbon(aes(fill = age_cat, ymin = conf.low, ymax = conf.high), 
              alpha = 0.2) +
  geom_line(aes(color = age_cat), linewidth = 1.2, linetype = "dashed") +
  geom_pointrange(aes(y = perc_male, 
                      ymin = perc_male - se, 
                      ymax = perc_male + se),
                  sexrat_summ) +
  geom_vline(xintercept = age_senesce - 0.5, linetype = "dashed") +
  scale_color_manual(values = c("#7fbc41", "#de77ae")) +
  scale_fill_manual(values = c("#7fbc41", "#de77ae")) +
  scale_y_continuous("Male offspring", labels = scales::percent) +
  labs(x = "Age (years)") +
  theme(legend.position = "none")
```

@@

```{r}
#| label: fig-pheno
#| fig-cap: "Molting gets shorter but breeding doesn't. A: Observed annual time allocation averaged over individuals. B: Raw data for breeding and molting durations (mean ± se) and predictions (mean and 95% CI) from negative binomial weighted by number of seals obersved per year."
#| fig-width: 9

phenology_n <- unique(seal_phenology$animalID)

timing_summary <- seal_phenology %>% 
  group_by(age) %>% 
  summarize(across(BA:MD, mean)) %>% 
  pivot_longer(cols = -age,  
               names_to = "event", 
               values_to = "doy") %>% 
  group_by(age) %>% 
  group_modify(\(data, keys) {
    tibble(event = c("Foraging", "Breeding haulout", "Post-breeding", "Molt haulout", "foraging2"),
           doy = c(data$doy, 365) - c(0, data$doy))
  }) %>% 
  ungroup() %>% 
  mutate(event = factor(event, levels = c("Foraging", 
                                          "Breeding haulout", 
                                          "Post-breeding", 
                                          "Molt haulout", 
                                          "foraging2")))

annual_plot <- ggplot(timing_summary, aes(x = age, y = doy, fill = event)) + 
  geom_area(position = position_stack(reverse = TRUE),
            color = NA) +
  geom_line(position = position_stack(reverse = TRUE),
            color = "white") +
  scale_fill_discrete(
    type = c("#829BD1", "#D05794", "#829BD1", "#E09A2D", "#829BD1"),
    breaks = c("Foraging", "Breeding haulout", "Molt haulout")
  ) + 
  scale_x_continuous("Maternal age (years)", expand = expansion(mult = 0)) +
  scale_y_continuous("Day of year", expand = expansion(mult = 0)) +
  theme(panel.spacing = unit(1, "lines"),
        legend.position = "bottom",
        legend.title = element_blank(),
        legend.text = element_text(size = 8),
        legend.key.size = unit(3, "mm"))

n_phenology <- seal_phenology %>% 
  count(year)

@@

duration_plot <- ggpredict(
  pheno_model, 
  terms = c("age10 [all]", "phase", "year [all]")
) %>% 
  as_tibble() %>% 
  transmute(age = x * 10,
            dur_days = predicted,
            dur_days_lwr = conf.low,
            dur_days_upr = conf.high,
            phase = group,
            year = as.numeric(as.character(facet))) %>% 
  left_join(n_phenology, by = "year") %>% 
  group_by(age, phase) %>% 
  summarize(across(starts_with("dur_days"), \(x) weighted.mean(x, n)),
            .groups = "drop") %>% 
  ggplot(aes(age)) +
  geom_ribbon(aes(ymin = dur_days_lwr, ymax = dur_days_upr, fill = phase),
              alpha = 0.25) +
  geom_pointrange(aes(y = dur_days, 
                      ymin = dur_days_lwr, 
                      ymax = dur_days_upr,
                      color = phase),
                  pheno_raw,
                  position = position_dodge(width = 0.5)) +
  geom_line(aes(y = dur_days, color = phase, linetype = phase)) +
  annotate("text", 12, 14, label = "Molting", color = "#E09A2D", hjust = 0) +
  annotate("text", 12, 32, label = "Breeding", color = "#D05794", hjust = 0) +
  scale_fill_manual(values = c("#D05794", "#E09A2D")) +
  scale_color_manual(values = c("#D05794", "#E09A2D")) +
  scale_linetype_manual(values = c("dashed", "solid")) +
  labs(x = "Maternal age (years)",
       y = "Phase duration (days)") +
  theme(legend.position = "none")

(annual_plot | duration_plot) + plot_annotation(tag_levels = "A") + plot_layout(widths = c(1.25, 2))

Sample size n = `r nrow(seal_phenology)` observations of `r n_distinct(phenology_n)` individuals.

@@

ggplot(bioage_pred_pop, aes(bioage, predicted)) +
  geom_ribbon(aes(fill = bioage_cat, ymin = conf.low, ymax = conf.high), 
              alpha = 0.2) +
  geom_line(aes(color = bioage_cat), linewidth = 1.2) +
  geom_line(aes(color = bioage_cat),
            bioage_pred_wgt, 
            linewidth = 1.2,
            linetype = "dotted") +
  geom_pointrange(aes(y = perc_breed, 
                      ymin = perc_breed - se, 
                      ymax = perc_breed + se),
                  bioage_summ) +
  geom_vline(xintercept = bioage_senesce - 0.5, linetype = "dashed") +
  scale_y_continuous("Breeding", labels = scales::percent) +
  scale_color_manual(values = c("#7fbc41", "#de77ae")) +
  scale_fill_manual(values = c("#7fbc41", "#de77ae")) +
  labs(x = "Biological age (years-to-death)") +
  theme(legend.position = "none")

>>>>

---
title: "Reproduction frequency and offspring survival decline in elephant seals past prime age"
format: 
  html: 
    echo: false
    fig-width: 7
    fig-height: 5
    code-fold: true
    code-tools: true
    warning: false
    toc: true
editor: visual
bibliography: references.bib
---

@@

#Create sample size data frame
n_breed <- sealdat %>% 
  filter(age <= 20) %>% 
  count(age)

# Create POPULATION-LEVEL (i.e. without rand effects) predictions
breed_pred_pop <- ggpredict(breed_age_mod, 
                            terms = c("age10 [all]", "age_cat")) %>% 
  as_tibble() %>% 
  mutate(age = x * 10 + age_senesce,
         age_cat = factor(group, levels = c("Young", "Old"))) %>% 
  filter((age_cat == "Young" & age < age_senesce) |
           (age_cat == "Old" & age >= age_senesce),
         age <= 20) %>% 
  left_join(n_breed, by = "age")

@@

ggplot(breed_pred_pop, aes(age, predicted)) +
  geom_line(aes(group = interaction(age_cat, year_fct)),
            breed_pred_years,
            alpha = 0.1) +
  geom_ribbon(aes(fill = age_cat, ymin = conf.low, ymax = conf.high), 
              alpha = 0.5) +
  geom_line(aes(color = age_cat), linewidth = 1.2) +
  geom_line(aes(color = age_cat),
            breed_pred_wgt, 
            linewidth = 1.2,
            linetype = "dashed") +
  geom_pointrange(aes(y = perc_breed,
                      ymin = perc_breed - se,
                      ymax = perc_breed + se),
                  breed_nonbreed) +
  geom_vline(xintercept = age_senesce - 0.5, linetype = "dashed") +
  scale_y_continuous("Breeding probability", labels = scales::percent) +
  scale_color_manual(values = c("#7fbc41", "#de77ae")) +
  scale_fill_manual(values = c("#7fbc41", "#de77ae")) +
  labs(x = "Age (years)") +
  theme(legend.position = "none") + 
  geom_text(aes(label = n, y = .55))

ggsave("outputs/repro_senesce.svg", width = 11, height = 6, units = "in")
```

@@

```{r}
#| label: fig-repro-age
#| fig-width: 8
#| fig-height: 8

@@

#Create sample size data frame
n_surv <- surv_recr_data %>% 
  group_by(age) %>% 
  count(age)

# Create pup survival POPULATION-LEVEL (i.e. without rand effects) predictions
surv_pred_pop <- ggpredict(
  pup_surv_mod, 
  terms = c("age10 [all]", "age_cat"),
  type = "fixed",
  interval = "confidence"
) %>% 
  as_tibble() %>% 
  mutate(age = x * 10 + age_senesce,
         age_cat = group) %>% 
  filter((age_cat == "Young" & age < age_senesce) |
           (age_cat == "Old" & age >= age_senesce),
         age <= 20) %>% 
  left_join(n_surv, by = "age")

@@

fig_surv <- ggplot(surv_pred_pop, aes(age, predicted)) +
  geom_line(aes(group = interaction(age_cat, year_fct)),
            surv_pred_years,
            alpha = 0.1) +
  geom_ribbon(aes(fill = age_cat, ymin = conf.low, ymax = conf.high), 
              alpha = 0.2) +
  geom_line(aes(color = age_cat, linetype = age_cat), linewidth = 1.2) +
  geom_pointrange(aes(y = perc_surv, 
                      ymin = perc_surv - se_surv, 
                      ymax = perc_surv + se_surv),
                  surv_recr_summ) +
  geom_vline(xintercept = age_senesce - 0.5, linetype = "dashed") +
  scale_y_continuous("Offspring survival", 
                     labels = scales::percent,
                     limits = c(0, 0.68)) +
  scale_color_manual(values = c("#7fbc41", "#de77ae")) +
  scale_fill_manual(values = c("#7fbc41", "#de77ae")) +
  scale_linetype_manual(values = c("dashed", "solid")) +
  labs(x = "Age (years)") +
  theme(legend.position = "none") + 
  geom_text(aes(label = n, y = .65))

#Create sample size data frame
n_recruit <- surv_recr_data %>% 
  filter(pupsex == "F") %>% 
  count(age)

# Create pup recruit POPULATION-LEVEL (i.e. without rand effects) predictions
recr_pred_pop <- ggpredict(
  pup_recr_mod, 
  terms = c("age10 [all]", "age_cat"),
  type = "fixed",
  interval = "confidence"
) %>% 
  as_tibble() %>% 
  mutate(age = x * 10 + age_senesce,
         age_cat = group) %>% 
  filter((age_cat == "Young" & age < age_senesce) |
           (age_cat == "Old" & age >= age_senesce),
         age <= 20) %>% 
  left_join(n_recruit, by = "age")

@@

fig_recr <- ggplot(recr_pred_pop, aes(age, predicted)) +
  geom_line(aes(group = interaction(age_cat, year_fct)),
            recr_pred_years,
            alpha = 0.1) +
  geom_ribbon(aes(fill = age_cat, ymin = conf.low, ymax = conf.high), 
              alpha = 0.2) +
  geom_line(aes(color = age_cat), linewidth = 1.2, linetype = "dashed") +
  geom_pointrange(aes(y = perc_recr, 
                      ymin = perc_recr - se_recr, 
                      ymax = perc_recr + se_recr),
                  surv_recr_summ) +
  geom_vline(xintercept = age_senesce - 0.5, linetype = "dashed") +
  scale_y_continuous("Offspring recruitment", 
                     labels = scales::percent,
                     limits = c(0, 0.68)) +
  scale_color_manual(values = c("#7fbc41", "#de77ae")) +
  scale_fill_manual(values = c("#7fbc41", "#de77ae")) +
  labs(x = "Age (years)") +
  theme(legend.position = "none") + 
  geom_text(aes(label = n, y = .65))

(fig_surv | fig_recr) + plot_annotation(tag_levels = "A") + plot_layout(ncol = 1, nrow = 2)

@@

#Make sample size data frame
n_sexrat <- pup_sex_data %>% 
  count(age)

# Create POPULATION-LEVEL (i.e. without rand effects) predictions
sexrat_pred <- ggpredict(sexrat_age_mod, 
                         terms = c("age10 [all]", "age_cat")) %>% 
  as_tibble() %>% 
  mutate(age = x * 10 + age_senesce,
         age_cat = factor(group, levels = c("Young", "Old"))) %>% 
  filter((age_cat == "Young" & age < age_senesce) |
           (age_cat == "Old" & age >= age_senesce)) %>% 
  left_join(n_sexrat, by = "age")

@@

ggplot(sexrat_pred, aes(age, predicted)) +
  geom_line(aes(group = interaction(age_cat, year_fct)),
            sexrat_pred_years,
            alpha = 0.1) +
  geom_ribbon(aes(fill = age_cat, ymin = conf.low, ymax = conf.high), 
              alpha = 0.2) +
  geom_line(aes(color = age_cat), linewidth = 1.2, linetype = "dashed") +
  geom_pointrange(aes(y = perc_male, 
                      ymin = perc_male - se, 
                      ymax = perc_male + se),
                  sexrat_summ) +
  geom_vline(xintercept = age_senesce - 0.5, linetype = "dashed") +
  scale_color_manual(values = c("#7fbc41", "#de77ae")) +
  scale_fill_manual(values = c("#7fbc41", "#de77ae")) +
  scale_y_continuous("Male offspring", labels = scales::percent) +
  labs(x = "Age (years)") +
  theme(legend.position = "none") +
  geom_text(aes(label = n, y = .95))

@@

```{r}
#| label: fig-pheno
#| fig-cap: "Molting gets shorter but breeding doesn't. A: Observed annual time allocation averaged over individuals. B: Raw data for breeding and molting durations (mean ± se) and predictions (mean and 95% CI) from negative binomial weighted by number of seals obersved per year."
#| fig-width: 4
#| fig-height: 9

phenology_unique_animals <- unique(seal_phenology$animalID)
n_phenology <- seal_phenology %>% 
  count(year)

#Make sample size data frame
n_phen <- seal_phenology %>% 
  count(age)

timing_summary <- seal_phenology %>% 
  group_by(age) %>% 
  summarize(across(BA:MD, mean)) %>% 
  pivot_longer(cols = -age,  
               names_to = "event", 
               values_to = "doy") %>% 
  group_by(age) %>% 
  group_modify(\(data, keys) {
    tibble(event = c("Foraging", "Breeding haulout", "Post-breeding", "Molt haulout", "foraging2"),
           doy = c(data$doy, 365) - c(0, data$doy))
  }) %>% 
  ungroup() %>% 
  mutate(event = factor(event, levels = c("Foraging", 
                                          "Breeding haulout", 
                                          "Post-breeding", 
                                          "Molt haulout", 
                                          "foraging2"))) %>% 
    left_join(n_phen, by = "age")

annual_plot <- ggplot(timing_summary, aes(x = age, y = doy, fill = event)) + 
  geom_area(position = position_stack(reverse = TRUE),
            color = NA) +
  geom_line(position = position_stack(reverse = TRUE),
            color = "white") +
  scale_fill_discrete(
    type = c("#829BD1", "#D05794", "#829BD1", "#E09A2D", "#829BD1"),
    breaks = c("Foraging", "Breeding haulout", "Molt haulout")
  ) + 
  scale_x_continuous("Maternal age (years)", expand = expansion(mult = 0)) +
  scale_y_continuous("Day of year", expand = expansion(mult = 0)) +
  theme(panel.spacing = unit(1, "lines"),
        legend.position = "bottom",
        legend.title = element_blank(),
        legend.text = element_text(size = 8),
        legend.key.size = unit(3, "mm")) 
  # geom_text(aes(label = n, color = "white", y = 300))

@@

phen_pred_years <- ggpredict(
  pheno_model,
  terms = c("age10 [all]", "phase", "year [all]"),
  type = "random",
  interval = "confidence"
) %>% 
  as_tibble() %>% 
  mutate(age = x * 10,
         phase = group)

breed_pheno_raw <- pheno_raw[pheno_raw$phase == "breeddur",]
molt_pheno_raw <- pheno_raw[pheno_raw$phase == "moltdur",]

breed_duration_plot <- ggpredict(
  pheno_model, 
  terms = c("age10 [all]", "phase", "year [all]")
) %>% 
  as_tibble() %>% 
  transmute(age = x * 10,
            dur_days = predicted,
            dur_days_lwr = conf.low,
            dur_days_upr = conf.high,
            phase = group,
            year = as.numeric(as.character(facet))) %>% 
  left_join(n_phenology, by = "year") %>% 
  group_by(age) %>% 
  filter(phase == "breeddur") %>% 
  summarize(across(starts_with("dur_days"), \(x) weighted.mean(x, n)),
            .groups = "drop") %>% 
  ggplot(aes(age)) +
  geom_line(aes(age, predicted, group = interaction(phase, facet)), 
            phen_pred_years, 
            alpha = 0.1) + 
  geom_ribbon(aes(ymin = dur_days_lwr, ymax = dur_days_upr),
              alpha = 0.25, 
              fill = "#D05794") +
  geom_pointrange(aes(y = dur_days, 
                      ymin = dur_days_lwr, 
                      ymax = dur_days_upr),
                  breed_pheno_raw,
                  position = position_dodge(width = 0.5), 
                  color = "#D05794") +
  geom_line(aes(y = dur_days), 
            linetype = "dashed", 
            color = "#D05794") +
  labs(x = "Maternal age (years)",
       y = "Breeding haul out (days)") +
  theme(legend.position = "none",
        axis.text.y = element_text(size = 8))

molt_duration_plot <- ggpredict(
  pheno_model,
  terms = c("age10 [all]", "phase", "year [all]")
) %>%
  as_tibble() %>%
  transmute(age = x * 10,
            dur_days = predicted,
            dur_days_lwr = conf.low,
            dur_days_upr = conf.high,
            phase = group,
            year = as.numeric(as.character(facet))) %>%
  left_join(n_phenology, by = "year") %>%
  group_by(age, phase) %>%
  filter(phase == "moltdur") %>%
  summarize(across(starts_with("dur_days"), \(x) weighted.mean(x, n)),
            .groups = "drop") %>%
  ggplot(aes(age)) +
  geom_line(aes(age, predicted, group = interaction(phase, facet)), 
            phen_pred_years, 
            alpha = 0.1) + 
  geom_ribbon(aes(ymin = dur_days_lwr, ymax = dur_days_upr),
              alpha = 0.25, 
              fill = "#E09A2D") +
  geom_pointrange(aes(y = dur_days, 
                      ymin = dur_days_lwr, 
                      ymax = dur_days_upr),
                  molt_pheno_raw,
                  position = position_dodge(width = 0.5), 
                  color = "#E09A2D") +
  geom_line(aes(y = dur_days), 
            color = "#E09A2D") +
  labs(x = "Maternal age (years)",
       y = "Molting haul out (days)") +
  theme(legend.position = "none", 
        axis.text.y = element_text(size = 8))

(annual_plot | breed_duration_plot | molt_duration_plot) + plot_annotation(tag_levels = "A") + plot_layout(ncol = 1, nrow = 3)
```

Sample size n = `r nrow(seal_phenology)` observations of `r n_distinct(phenology_unique_animals)` individuals.

@@

ggplot(bioage_pred_pop, aes(bioage, predicted)) +
  geom_ribbon(aes(fill = bioage_cat, ymin = conf.low, ymax = conf.high), 
              alpha = 0.2) +
  geom_line(aes(color = bioage_cat), linewidth = 1.2, linetype = "dashed") +
  geom_line(aes(color = bioage_cat),
            bioage_pred_wgt, 
            linewidth = 1.2,
            linetype = "dotted") +
  geom_pointrange(aes(y = perc_breed, 
                      ymin = perc_breed - se, 
                      ymax = perc_breed + se),
                  bioage_summ) +
  geom_vline(xintercept = bioage_senesce - 0.5, linetype = "dashed") +
  scale_y_continuous("Breeding probability", labels = scales::percent, limits = c(.7, 1)) +
  scale_color_manual(values = c("#7fbc41", "#de77ae")) +
  scale_fill_manual(values = c("#7fbc41", "#de77ae")) +
  scale_x_continuous(limits = c(-17, 0)) + 
  labs(x = "Biological age (years-to-death)") +
  theme(legend.position = "none")
